Joe Biden won popular votes in 2024 US Presidential Election

### 2024-03-09 outputs/paper.qmd
tests, parquet

---
title: "Joe Biden won popular votes in 2024 US Presidential Election"
format: pdf
ate: "9 March 2024"
date-format: "D MMMM YYYY"
number-sections: true
thanks: "Code and data in this analysis is available at: "
toc: true

---
```{r}
#| include: false
# install.packages('dplyr')
# install.packages('ggplot2')
# install.packages('knitr')
# install.packages('statebins')
# install.packages('modelsummary')
# install.packages('broom')
# install.packages("here")
# install.packages("kableExtra")

library(dplyr)
library(ggplot2)
library(knitr)
library(statebins)
library(modelsummary)
library(broom)
library(readr)
library(here)
library(kableExtra)
```

```{r}
#| include: false
data_ipums_clean <-
  read_csv(
    file = here("inputs/IPUMS/cleaned_population_data.csv"),
    show_col_types = FALSE
  )

>>>>

---
title: "Joe Biden won popular votes in 2024 US Presidential Election"
format: pdf
date: "9 March 2024"
date-format: "D MMMM YYYY"
number-sections: true
thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/2024prediction_USPresidentialElection"
toc: true

---
```{r}
#| include: false
library(dplyr)
library(ggplot2)
library(knitr)
library(statebins)
library(modelsummary)
library(broom)
library(readr)
library(here)
library(kableExtra)
library(arrow)
```

```{r}
#| include: false
# data_ipums_clean <- read_parquet(file = "inputs/IPUMS/cleaned_population_data.parquet")
# data_app_clean <- read_parquet(file = "inputs/APP/cleaned_sample_data.parquet")
# data_app_clean_20 <- read_parquet(file = "inputs/APP/cleaned_sample_data_20.parquet")
# statevote2020 <- read_parquet(file = "inputs/Kaggle/cleaned_actual_data_20.parquet")
# data_app_raw <- read_parquet(file = "inputs/APP/raw_sample_data.parquet")
data_ipums_clean <-
  read_csv(
    file = here("inputs/IPUMS/cleaned_population_data.csv"),
    show_col_types = FALSE
  )
